---
title: "\\vspace{-1cm}  Mushroom Classification"
subtitle: "— **Siham Elmali and Mary Washington** —"
geometry: "right = 3cm, left = 3cm, top = 2cm, bottom = 2cm"
abstract: \noindent Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
output:
  pdf_document: default
header-includes: 
  - \usepackage{setspace}\doublespacing
  - \usepackage{placeins}
---
$\vspace{-0.5cm}$

```{r initial-settings, include=FALSE}
# Settings
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.pos = 'H')
```

```{r installing-packages, warning = FALSE, message=FALSE}

# Check if packages are installed. If not, install them.
install.packages <- function(pkg) {
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg)) {
        install.packages(new.pkg)
    }
}

packages <- c("ggplot2", "mcmcplots", "knitr","xtable", "kableExtra","klaR","kernlab","kknn",
              "reshape2", "devtools","MASS","glmnet", "lares", "caret","GGally",
              "splines", "class", "dplyr", "PerformanceAnalytics",  "factoextra")

install.packages(packages)
library(mcmcplots)                            
library(knitr)                               
library(kableExtra)                         
library(ggplot2)
library(reshape2)
library(devtools)
library(splines)
library(extrafont)
library(xtable)
library(dplyr)
library(akima)
library(plotly)
library(factoextra)
library(GGally)
library(tidyr)
options(kableExtra.latex.load_packages = FALSE)
loadfonts()
```

## Introduction



## Problem Statement and Data set

1. cap-diameter (m): float number in cm

2. cap-shape (n): bell=b, conical=c, convex=x, flat=f,sunken=s, spherical=p, others=o

3. cap-surface (n):     fibrous=i, grooves=g, scaly=y, smooth=s,
						shiny=h, leathery=l, silky=k, sticky=t,
						wrinkled=w, fleshy=e
						
4. cap-color (n):       brown=n, buff=b, gray=g, green=r, pink=p,
						purple=u, red=e, white=w, yellow=y, blue=l, 
						orange=o,  black=k
						
5. does-bruise-bleed (n):	bruises-or-bleeding=t,no=f

6. gill-attachment (n):      adnate=a, adnexed=x, decurrent=d, free=e, sinuate=s, pores=p, none=f, unknown=?

7. gill-spacing (n):         close=c, distant=d, none=f

8. gill-color (n):           see cap-color + none=f

9. stem-height (m):			float number in cm

10. stem-width (m):			float number in mm 
  
11. stem-root (n):           bulbous=b, swollen=s, club=c, cup=u, equal=e,rhizomorphs=z, rooted=r

12. stem-surface (n): 		see cap-surface + none=f

13. stem-color (n):			see cap-color + none=f

14. veil-type (n):           partial=p, universal=u

15. veil-color (n):          see cap-color + none=f

16. has-ring (n):            ring=t, none=f

17. ring-type (n):           cobwebby=c, evanescent=e, flaring=r, grooved=g, 
					        large=l, pendant=p, sheathing=s, zone=z, scaly=y, movable=m, none=f, unknown=?
							
18. spore-print-color (n):   see cap color

19. habitat (n):             grasses=g, leaves=l, meadows=m, paths=p, heaths=h,
                             urban=u, waste=w, woods=d
							 
20. season (n):				spring=s, summer=u, autumn=a, winter=w

  
## Exploratory Data Analysis

```{r}
# read data
mushroom <- read.table("C:/Users/Siham/OneDrive/Desktop/OMSA/DMSL/project/MushroomDataset/secondary_data.csv", head=T, sep=";")

colnames(mushroom)

# convert all columns to factors
library(tidyverse)
mushroom <- mushroom %>% map_df(function(.x) as.factor(.x))
```

```{r fig1, fig.width=12,fig.height=7,fig.cap="\\label{fig:fig1}Pairs plot"}

# ggpairs(temp,legend = 1, bins=45,
#                mapping = ggplot2::aes(colour=as.factor(class01)))
#                theme(legend.position = "bottom")
               
               
ggplot(mushroom, aes(x = cap.surface, y = cap.color, col = class)) + 
  geom_jitter(alpha = 0.5) + 
  scale_color_manual(breaks = c("e", "p"), 
                     values = c("green", "red"))


ggplot(mushroom, aes(x = season, y = class , col = class)) + 
  geom_jitter(alpha = 0.5) + 
  scale_color_manual(breaks = c("e", "p"), 
                     values = c("green", "red"))

ggplot(mushroom, aes(x = habitat, y = class , col = class)) + 
  geom_jitter(alpha = 0.5) + 
  scale_color_manual(breaks = c("e", "p"), 
                     values = c("green", "red"))
```

## Results


## Conclusion and Findings


## References
